The Effects of the 2023 Rule Changes in Major League Baseball

### 2023-11-14 manuscript/paper.tex
changed the roadmap in the Intro section

% roadmap
The rest of the paper is organized as follows.
A literature review of relevant works will be examined in Section~\ref{sec:lit}.
The data used in the study will be presented in Section~\ref{sec:data}.
The methods are described in Section~\ref{sec:meth}.
The results are reported in Section~\ref{sec:resu}.
A discussion concludes in Section~\ref{sec:disc}.

>>>>

% roadmap
The rest of the paper is organized as follows.
A literature review of relevant works will be examined in Section~\ref{sec:lit}.
The data used in the study will be presented in Section~\ref{sec:data}.
The statistical methods and hypotheses are described in Section~\ref{sec:meth}.
The results and findings are reported in Section~\ref{sec:resu}.
An overall discussion concludes in Section~\ref{sec:disc}.
